PM Mungbean meta-analysis

### 2021-03-02 01_TrialsForInclusionInAnalysis.Rmd
change devtools:: to remotes::

if (!require("theme.usq"))
   devtools::install_github("adamhsparks/theme.usq")
library(theme.usq)
theme_set(theme_usq()
)
```
Trials testing fungicide efficacy on powdery mildew in mungbean in the Grains Research and Development Corporation (GRDC) northern grains region were sourced for a meta-analysis.

>>>>

if (!require("theme.usq"))
   remotes::install_github("adamhsparks/theme.usq")
library(theme.usq)
theme_set(theme_usq()
)
```
Trials testing fungicide efficacy on powdery mildew in mungbean in the Grains Research and Development Corporation (GRDC) northern grains region were sourced for a meta-analysis.

### 2021-03-02 02_Preliminary_analysis.Rmd
Edit headings
change devtools:: to remotes::

if (!require("theme.usq"))
   devtools::install_github("adamhsparks/theme.usq")
library(theme.usq)
theme_set(theme_usq()
)
load("cache/ImportDataAndSelectTrials01.Rdata")
```

@@

## Trial summaries statistics

>>>>

if (!require("theme.usq"))
   remotes::install_github("adamhsparks/theme.usq")
library(theme.usq)
theme_set(theme_usq()
)
load("cache/ImportDataAndSelectTrials01.Rdata")
```

@@

## Trial summary statistics
